Local PCA results

### 2016-05-28 medicago/summarize_run.Rmd
added corner plots to summarize_run.Rmd

@@

Now, we'll look at PCA plots from the extracted corners.
(warning: takes awhile and a lot of RAM)
```{r corner_pca, cache=TRUE}
corner.npc <- 4
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
            regions[ mds.corners[,k], ]
    } )
corner.pca <- lapply( corner.regions, function (reg) {
            geno <- multi_vcf_query( chrom.list=chroms, file=bcf.files, regions=reg )
            cov_pca(geno,k=corner.npc,w=opt$weights)
    } )
```

First, here are the first `r corner.npc` PCs for each corner, together:
```{r plot_corner_pca, fig.width=3*fig.dim}
for (k in seq_along(mds.corners)) {
    vectors <- matrix( corner.pca[[k]][-(1:(1+corner.npc))], ncol=corner.npc )
    colnames(vectors) <- paste("PC", 1:corner.npc)
    pairs(vectors)
}
```

>>>>

sample.ids <- vcf_samples(bcf.files[1])
samp.file <- file.path( "..", "..", "data", "sample_info.tsv" )
samps <- read.table(samp.file,sep="\t",header=TRUE)
samps <- droplevels( samps[match(gsub("-I$","",sample.ids),samps$ID),] )

@@

Now, we'll look at PCA plots from the extracted corners.
(this is done without a ton of memory by accumulating the covariance matrix in `running_cov`):
```{r corner_pca, cache=TRUE}
corner.npc <- 4
corner.regions <- lapply( 1:ncol(mds.corners), function (k) {
            regions[ mds.corners[,k],]
    } )
corner.covmats <- lapply( 1:ncol(mds.corners), function (k) {
            reg <- regions[ mds.corners[,k], ]
            qfun <- multi_vcf_query_fn( chrom.list=chroms, file=bcf.files, regions=reg )
            running_cov(qfun,1:nrow(reg))
        } )
corner.pca <- lapply( corner.covmats, function (covmat) {
            cov_pca(covmat=covmat,k=corner.npc,w=opt$weights)
    } )
```

Here is the color scheme:
```{r pop_colors, fig.height=2*fig.dim}
pop.names <- levels(samps$Country.of.Origin)
pop.cols <- rainbow_hcl(nlevels(samps$Country.of.Origin))
pop.pch <- seq_len(nlevels(samps$Country.of.Origin))
plot( rep(1,length(pop.names)), seq_along(pop.names), pch=pop.pch, col=pop.cols, xlim=c(0,length(pop.names)),
       xlab='', ylab='', xaxt='n', yaxt='n' )
text( rep(1,length(pop.names)), seq_along(pop.names), labels=pop.names, pos=4 )
```

Here are all pairwise plots of the first `r corner.npc` PCs for each of the three corners:
```{r plot_corner_pca, fig.width=3*fig.dim}
layout(t(1:3))
for (i in 1:(corner.npc-1)) {
    for (j in (i+1):corner.npc) {
        for (k in 1:ncol(mds.corners)) {
            vectors <- matrix( corner.pca[[k]][-(1:(1+corner.npc))], ncol=corner.npc )[,c(i,j)]
            colnames(vectors) <- paste("PC", c(i,j))
            plot(vectors, pch=pop.pch[samps$Country.of.Origin], 
                    col=pop.cols[samps$Country.of.Origin] )
            if (i==1 && j==2) {
                mtext(paste("corner",k),side=3,cex=2)
            }
        }
    }
}
```
